---
title: "Clinical Digital Twin — Simulation Summary"
output:
  html_document:
    theme: flatly
    toc: false
params:
  data: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
d <- params$data
stopifnot(!is.null(d))
```

## `r d$meta$simulation_id` — branch `r d$meta$branch`

`r d$meta$days_run` day(s) &middot; overall gate outcome:
**`r toupper(d$gate_outcome)`** &middot; generated `r d$meta$generated_at`.

All data is **synthetic**. This is a summary (not a full per-resident report):
it records which checkpoints passed, the obstacles encountered, and what the
run tolerated versus what halted it.

### Checkpoint tally

| Status | Count |
|---|---|
| pass | `r d$status_counts[["pass"]]` |
| warn | `r d$status_counts[["warn"]]` |
| fail | `r d$status_counts[["fail"]]` |

```{r failed-days, results='asis'}
if (length(d$failed_days) == 0) {
  cat("**No day failed the gate.** The run completed all attempted days.\n")
} else {
  cat(sprintf("**Gate failed on day(s):** %s.\n",
    paste(d$failed_days, collapse = ", ")))
}
```

### Obstacles encountered

```{r obstacles, results='asis'}
if (length(d$obstacles) == 0) {
  cat("_No warnings or failures were recorded — a clean run._\n")
} else {
  for (o in d$obstacles) cat(sprintf("- %s\n", o))
}
```

---
_Synthetic data only. Not for clinical use._
