---
title: "Clinical Digital Twin — Simulation Summary"
output:
  html_document:
    theme: flatly
    toc: false
params:
  data: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
d <- params$data
stopifnot(!is.null(d))
```

## `r d$meta$simulation_id` — branch `r d$meta$branch`

`r d$meta$days_run` day(s) &middot; overall gate outcome:
**`r toupper(d$gate_outcome)`** &middot; generated `r d$meta$generated_at`.

All data is **synthetic**. This is a summary (not a full per-resident report):
it records which checkpoints passed, the obstacles encountered, and what the
run tolerated versus what halted it.

### Checkpoint tally

| Status | Count |
|---|---|
| pass | `r d$status_counts[["pass"]]` |
| warn | `r d$status_counts[["warn"]]` |
| fail | `r d$status_counts[["fail"]]` |

```{r failed-days, results='asis'}
if (length(d$failed_days) == 0) {
  cat("**No day failed the gate.** The run completed all attempted days.\n")
} else {
  cat(sprintf("**Gate failed on day(s):** %s.\n",
    paste(d$failed_days, collapse = ", ")))
}
```

### Obstacles encountered

```{r obstacles, results='asis'}
if (length(d$obstacles) == 0) {
  cat("_No warnings or failures were recorded — a clean run._\n")
} else {
  for (o in d$obstacles) cat(sprintf("- %s\n", o))
}
```

### Validation axes

```{r validation, results='asis'}
v <- d$validation
sc <- function(x) sprintf("pass %d / warn %d / fail %d",
  x[["pass"]], x[["warn"]], x[["fail"]])
cat("**(i) Technical integrity**\n\n")
cat(sprintf("- Biological gate: %s\n", sc(v$technical$biological)))
cat(sprintf("- Model-output gate: %s\n", sc(v$technical$model_output)))
cat(sprintf("- All predictions in [0,1]: **%s**\n\n",
  v$technical$all_predictions_in_range))
ex <- v$experimental
cat("**(ii) Experimental validity (observable side)**\n\n")
cat(sprintf("- Branch **%s**; intervention fired: **%s**%s\n",
  ex$branch, ex$intervention_fired,
  if (isTRUE(ex$intervention_count > 0))
    sprintf(" (%d logged preventive review(s))", ex$intervention_count)
  else ""))
cat(sprintf("- _%s_\n\n", ex$note))
sf <- v$safety
cat("**(iv) Safety / leakage**\n\n")
cat(sprintf("- Leaked fields in payload: **%d**; ground-truth getter exported: **%s**\n",
  length(sf$payload_leak_hits), sf$ground_truth_getter_exists))
cat(sprintf("- **Attestation: %s**\n",
  if (isTRUE(sf$attestation)) "PASS" else "REVIEW"))
```

---
_Synthetic data only. Not for clinical use._
