---
title: "Clinical Digital Twin — Full Simulation Report"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
params:
  data: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
  fig.width = 8, fig.height = 3.2)
d <- params$data
stopifnot(!is.null(d))
```

## Executive summary

**Run:** `` `r d$meta$simulation_id` `` &middot; branch **`` `r d$meta$branch` ``**
&middot; `r d$meta$days_run` day(s) &middot; `r d$meta$n_patients` residents
&middot; generated `r d$meta$generated_at`.

This is a fully auditable account of one branch of the multi-agent simulation
over the fixed 10-resident module. All data is **synthetic**.

| Metric | Value |
|---|---|
| Days completed | `r d$exec$days_run` |
| Model predictions written | `r d$exec$n_predictions` |
| Checkpoints passed | `r d$exec$checkpoints_pass` |
| Checkpoints warned | `r d$exec$checkpoints_warn` |
| Checkpoints failed | `r d$exec$checkpoints_fail` |
| Degraded agent decisions (invalid → prior reused) | `r d$exec$degraded_decisions` |
| Highest 7-day risk resident | `` `r d$exec$highest_risk_patient` `` |

## Per-resident risk trajectories

Each panel plots the model's reported fall probability over the run: 24-hour
(blue) and 7-day (orange). Dates run left→right; probability on the y-axis.

```{r per-patient, results='asis'}
theme_cols <- c(p24 = "#2b6cb0", p7 = "#dd6b20")
for (pid in names(d$patients)) {
  p <- d$patients[[pid]]
  cat(sprintf("\n\n### %s (%s)\n\n", pid, p$name))
  if (length(p$day) == 0) {
    cat("_No predictions recorded for this resident._\n")
    next
  }
  cat(sprintf(
    "Final tiers: 24h **%s**, 7d **%s** &middot; peak 7d risk %.1f%%.\n\n",
    p$final_tier_24h, p$final_tier_7d, 100 * p$peak_p_7d))
  ylim <- range(c(0, p$p_24h, p$p_7d), na.rm = TRUE)
  if (diff(ylim) == 0) ylim <- ylim + c(0, 0.01)
  plot(p$day, p$p_24h, type = "b", pch = 19, col = theme_cols[["p24"]],
    ylim = ylim, xlab = "Simulation day", ylab = "P(fall)",
    main = sprintf("%s — reported fall risk", pid), las = 1,
    cex = 0.6, lwd = 2)
  lines(p$day, p$p_7d, type = "b", pch = 17, col = theme_cols[["p7"]],
    cex = 0.6, lwd = 2)
  legend("topleft", legend = c("24-hour", "7-day"),
    col = theme_cols, pch = c(19, 17), lwd = 2, bty = "n", cex = 0.85)
}
```

## Checkpoint gate log

Every daily checkpoint step and its status. `pass`/`warn` proceed; `fail`
halts the run.

```{r checkpoints}
ck <- d$checkpoints
if (nrow(ck) == 0) {
  cat("_No checkpoints logged._")
} else {
  knitr::kable(ck[, c("day", "step", "status", "detail")],
    col.names = c("Day", "Step", "Status", "Detail"))
}
```

## Traceability appendix

Per-day counts of agent decisions and model predictions, plus how many
decisions were degraded (invalid agent output → prior-day decision reused).
This is the audit trail linking each simulated day to its persisted rows.

```{r traceability}
tr <- d$traceability
if (nrow(tr) == 0) {
  cat("_No decisions recorded._")
} else {
  knitr::kable(tr,
    col.names = c("Day", "Decisions", "Invalid (reused)", "Predictions"))
}
```

---
_Synthetic data only. Not for clinical use._
